% !TeX root = JaredStemper_Resume.tex
%-------------------------------------
% Author: Jared Stemper (jaredstemper.com)
% Derived from: Leslie Cheng's "LaTeX Resume for Software Engineers" and Trey Hunner's "Medium Length Professional CV"
% License: MIT
%-------------------------------------

%--------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS 
%--------------------------------------------------------------------------

\documentclass{resume}

\begin{document}

%---------------------------------------------------- HEADER ----------------------------------------------------

\headertype{\linkedin}{\github}{}{\email}{\phone}{} % Set the order of items

\vspace{-10pt} % negative value to push the body up


%-------------------------------------------------- EXPERIENCE --------------------------------------------------
\section{Experience}
  %   \resumeEntryStart
  %     \resumeEntryTSDL
  %       {}{}
  %       {}{}
  %     \resumeItemListStart
  %       \resumeItem {}
  %       \resumeItem {}
  %       \resumeItem {}
  %     \resumeItemListEnd
  %   \resumeEntryEnd
     
    \resumeEntryStart
      \resumeEntryTSDL
        {Offensive Security Engineer}{September 2024 -- Present}
        {TikTok USDS}{New York, NY}
      \resumeItemListStart
        \resumeItem {\countourBold{Architected \& deployed a distributed, event-driven microservices platform} using Golang, Kafka, \& Redis, achieving a \countourBold{98\% reduction in runtime} for telemetry collection across millions of nodes.}
        \resumeItem {\countourBold{Engineered an extensible, decoupled analysis layer} with Open Policy Agent (OPA) identifying \countourBold{2,000+ control gaps} in MVP that provided continuous validation \& \countourBold{automated regression testing} against vulnerabilities.}
        \resumeItem {Orchestrated \countourBold{CI/CD pipelines} for complex, multi-system deployments \& developed custom automation tooling, such as an API-to-Go code generator that accelerated offensive testing workflows.}
        \resumeItem {Led systemic vulnerability research across production networks and bespoke applications, uncovering critical flaws in complex authentication flows and custom business logic.}
      \resumeItemListEnd
    \resumeEntryEnd

  % \resumeEntryStart
  %   \resumeEntryTSDL
  %   {Senior Penetration Tester}{July 2024 -- July 2024}
  %   {Sikich LLC}{Remote}
  %   \resumeItemListStart
  %     \resumeItem {Performed \countourBold{red team}, \countourBold{physical penetration}, \& \countourBold{network} penetration testing as a technical lead of the close access and network exploitation teams.}
  %     \resumeItem {Mentored and led testing across \countourBold{web application}, \countourBold{LLM/AI} models, wireless network, social-engineering, cloud penetration testing, \& configuration review assessments (AWS).}
  %   \resumeItemListEnd
  % \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
    {Offensive Cybersecurity Consultant}{July 2021 -- July 2024}
    {RSM US LLP}{Chicago, IL}
    \resumeItemListStart
      \resumeItem {Performed \countourBold{red team}, \countourBold{physical penetration}, \& \countourBold{network} penetration testing as a technical lead of the close access and network exploitation teams.}
      \resumeItem {Mentored and led testing across \countourBold{web application}, \countourBold{LLM/AI} models, wireless network, social-engineering, cloud penetration testing, \& configuration review assessments (AWS).}
      \resumeItem {Developed \countourBold{Python} and \countourBold{Tmux} automation framework to streamline \countourBold{network penetration testing} organization \& automating attacks; reducing start-up time by 85\% for testers.}
      \resumeItem {Built modular scanner and reporting utility with \countourBold{Python} and \countourBold{Docker} to asynchronously run security tooling, including \countourBold{AWS} configuration and code review, before consolidating output into standardized findings for reporting.}
      \resumeItem {Created a long-range \countourBold{RFID} badge cloner using microcontroller devices with live credential reading through a \countourBold{Raspberry Pi} wireless AP.}
      \resumeItem {Provided actionable remediation recommendations to client executives by delivering breach vector reports, enabling risk reduction \& minimizing liability exposure for Fortune 10 technology companies, Fortune 500 financial institutions, \& private clients.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
    {Security Software Engineering Intern}{May 2020 -- Dec 2020}
    {Synopsys}{Bloomington, IN}
    \resumeItemListStart
      \resumeItem {Automated AB-testing analysis through \countourBold{Python} scripting report comparison, resulting in a 40\% reduction in manager analysis time.}
      \resumeItem {Aggregated assessment data across Netsparker, AppScan, \& \countourBold{BurpSuite} through \countourBold{Jira} \& \countourBold{PostgreSQL}, facilitating tracking of vulnerability trends.}
      \resumeItem {Designed \& implemented an automated Tableau storyboard for senior managers \& C-level to track trends across assessments.}
    \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
    {Penetration Security Consulting Intern}{Jun 2019 -- Aug 2019}
    {RSM US LLP}{Chicago, IL}
    \resumeItemListStart
      \resumeItem{Supported security engagements in network/web pentesting, developing automation scripts, \& assisting NIST CSF compliance assessments.}
      % \resumeItem {Performed assisted network and web application penetration testing on client engagements.}
      % \resumeItem {Developed Visual Basic macros \& Python scripts for automating drafting/draft handling in Excel.}
      % \resumeItem {Measured client compliance within NIST CSF assessments through direct communication with key stakeholders.}
      \resumeItemListEnd
  \resumeEntryEnd

  \resumeEntryStart
    \resumeEntryTSDL
    {Undergraduate Instructor: Intro. to Python Programming}{Sep 2018 -- Jun 2020}
    {Indiana University}{Bloomington, IN}
    \resumeItemListStart
      \resumeItem{Developed \& maintained Python autograding tools while supporting instruction of 200+ students through extensive Python exercises \& labs.}
      % \resumeItem {Developed \& maintained Python scripts to facilitate autograding of 200+ students.}
      % \resumeItem {Led and assisted instruction for student groups of 20-45 through 55 exercises \& labs regarding Python.}
    \resumeItemListEnd
  \resumeEntryEnd

%-------------------------------------------------- EDUCATION --------------------------------------------------
\section{Education}

  \resumeEntryStart
    \resumeEntryTSDL
    {B.S. in Computer Science}{Aug 2017 -- May 2021}
    {Indiana University}{Bloomington, IN}
      {\newline{}\newline{}\scriptsize \textit{ \footnotesize{Relevant Courses: Data Structures, Machine Learning, Relational Databases, Networking, C and Unix, Discrete Mathematics, Linear Algebra}}}
  \resumeEntryEnd

%-------------------------------------------------- TECHNICAL SKILLS --------------------------------------------------
\section{Technical Skills}
 \resumeTechnicalEntryStart
  \resumeEntryS{Languages:} {Golang/Go, Python, C/C++, SQL, JavaScript, HTML/CSS, Unix Bash}
  \resumeEntryS{Systems/Frameworks:} {OPA, RDS, Kafka, Redis, Hertz, FaaS, HIVE}
  \resumeEntryS{Certifications:} {PNPT, SANS GPCS, CompTIA CySA+, AWS Certified Cloud Practitioner}
  \resumeEntryS{Security:} {Red Team, Internal/External Network, Web Application, Physical, \& Social Engineering Penetration Testing}
  \resumeEntryS{Miscellaneous:} {AWS, Docker, Containerization, Linux, Tenable Nessus, Forklift-certified, Cobalt Strike}
  \resumeTechnicalEntryEnd

%-------------------------------------------------- PROJECTS --------------------------------------------------
\section{Projects}
  \resumeProjectEntryStart
    \resumeEntryTD
      {\scylla}{2023 - Present}
    \resumeItemListStart
      \resumeItem {Orchestration and automation tool developed using Bash and Python to support efficient and consistent internal network penetration testing.}
    \resumeItemListEnd
  \resumeProjectEntryEnd 
  
  \resumeProjectEntryStart
    \resumeEntryTD
      {\nixRouter}{2025}
    \resumeItemListStart
      \resumeItem {Infrastructure-as-code router implementation fethiwaturing default-deny nftables rulesets, stateful packet inspection, IPv6 blocking, \& network isolation to support safe adversary simulation and exploit development environments.}
    \resumeItemListEnd
  \resumeProjectEntryEnd 
  
%  \resumeProjectEntryStart
%    \resumeEntryTD
%      {\charybdis}{2023 - Present}
%    \resumeItemListStart
%      \resumeItem {Asynchronously scan and ingest data for static code and cloud account configuration testing- spitting out human-readable, highly customizable reporting templates.}
%    \resumeItemListEnd
%  \resumeProjectEntryEnd
  
  \resumeProjectEntryStart
    \resumeEntryTD
      {\passmasker}{2024}
    \resumeItemListStart
      \resumeItem {Analyze a list of passwords using novel bucket-sort implementation to improve computation by 40\% and provide an analysis of the the passwords into a mask ingestible to hashcat.}
    \resumeItemListEnd
  \resumeProjectEntryEnd
  
  % \resumeProjectEntryStart
  %   \resumeEntryTD
  %     {\metasploitlab}{2021}
  %   \resumeItemListStart
  %     \resumeItem {Developed a docker network connecting a Kali OS to a Metasploitable2 OS to facilitate pen testing practice.}
  %   \resumeItemListEnd
  % \resumeProjectEntryEnd

  \resumeProjectEntryStart
    \resumeEntryTD
      {\torresearchproject}{2019}
    \resumeItemListStart  
      \resumeItem {Measured comparative data sets to determine Tor browser's anti-fingerprinting capabilities and develop an algorithm to bypass controls.}
    \resumeItemListEnd  
  \resumeProjectEntryEnd  

  
%-------------------------------------------------- Volunteering --------------------------------------------------
\section{Volunteering}

  
\resumeEntryStart
    \resumeEntryTD
      {\#HashtagLunchbag Volunteer}{2022 - 2024}
    \resumeItemListStart
      \resumeItem {Packed lunches to help prepare meals for Pacific Garden Mission homeless shelter.}
    \resumeItemListEnd
  \resumeEntryEnd
  
  
  


\end{document}